Price of Anarchy for Mean Field Games

### 2018-08-03 PoA.tex
added comment about Theorem 2 in flocking example

\subsection{\textbf{A Particular Example: Flocking}}
Mean field game models of flocking have been proposed in the literature by Nourian et al \cite{nourian2010synthesis}\cite{nourian2011mean}. Here we consider a slightly different formulation as described in Section 3.6.1 of the book \cite{Carmona_book}. A representative bird in the flock controls their velocity, $X_t$, through the drift:
\begin{equation*}
    b(t,x,\mu,\alpha,\nu)=\alpha.
\end{equation*}
They choose the control with two goals in mind: to minimize their kinetic energy put into their control, and to align their velocity with the average velocity of the group. Thus, they consider the cost functions given by:
\begin{equation*}
\begin{split}
    f(t,x,\mu,\alpha,\nu)&=\frac{1}{2}\left(\bar{q}|x-s\bar{\mu}|^2 +\alpha^2 \right), \\
    g(x,\mu)&=0.
\end{split}
\end{equation*}

In our general linear quadratic formulation, this is equivalent to taking $b_1=0$, $\bar{b}_1=0$, $b_2=1$, $\bar{b}_2=0$, $q=0$, $s=1$, $r=1$, $\bar{r}=0$, and $\bar{s}=0$. Note that for these values of the parameters, the assumptions of Theorem \ref{th:exist_uniq} and Corollary \ref{corollary_1} are satisfied. Therefore, $PoA=1$. In fact, if we took the state space to be $\mathbb{R}^d$ instead of $\mathbb{R}$, the result would still hold.

>>>>

\subsection{\textbf{A Particular Example: Flocking}}
Mean field game models of flocking have been proposed in the literature by Nourian et al \cite{nourian2010synthesis}\cite{nourian2011mean}. Here we consider a slightly different formulation as described in Section 3.6.1 of the book \cite{Carmona_book}. A representative bird in the flock controls their velocity, $X_t$, through the drift:
\begin{equation*}
    b(t,x,\mu,\alpha,\nu)=\alpha.
\end{equation*}
Suppose the initial condition is $X_0=1$. They choose their control with two goals in mind: to minimize their effort put into their control, and to align their velocity with the average velocity of the group. Thus, they consider the cost functions given by:
\begin{equation*}
\begin{split}
    f(t,x,\mu,\alpha,\nu)&=\frac{1}{2}\left(|x-\bar{\mu}|^2 +\alpha^2 \right), \\
    g(x,\mu)&=0.
\end{split}
\end{equation*}

In our general linear quadratic formulation, this is equivalent to taking $\xi \equiv 1$, $b_1=0$, $\bar{b}_1=0$, $b_2=1$, $\bar{b}_2=0$, $q=0$, $\bar{q}=1$, $s=1$, $r=1$, $\bar{r}=0$, $\bar{s}=0$, $q_T=0$, $\bar{q}_T=0$, and $s_T=0$. Note that for these values of the parameters, the assumptions of Theorem \ref{th:exist_uniq} and Corollary \ref{corollary_1} are satisfied. Therefore, $PoA=1$. We also see that $D^u=0=D^w$ and $C^u=0=C^w$, and therefore, Theorem \ref{thm:PoA_equivalent_1} also implies $PoA=1$. In fact, if we took the state space to be $\mathbb{R}^d$ instead of $\mathbb{R}$, the result would still hold.
